\chapter*{Acknowledgements}
This is the fourth thesis of my \textit{curriculum studiorum}. The previous ones were written for my Bachelor's, Master's and Doctoral degrees. Contrarily to the others, this thesis is not on physics and astronomy. However, just like the others, it includes my acknowledgements to the persons who most supported me in this endeavour. I am very thankful to:
  
\begin{itemize}
 \item Daniela Ovadia for supervising the work I present in this thesis;
 \item Elisabeth Schmid and Elena Gaboardi for the possibility to carry out an internship at the youris.com media agency in Milan. It was a unique chance to learn about science communication from motivated professionals and to discover the FET environment, which inspired me for this thesis; 
 \item Alessandra Barbieri from youris.com for running on NUVI the monitoring activity outlined in section \ref{Mentions_of_HPC_profiles};
 \item All other colleagues at youris.com I had the pleasure to know and work with: Noemi Ancona, Marcello Bardellini, Giulio Bordonaro, Alice De Ferrari, Angelique Lusuan, Mario Martinoli, Charlotte Michi, Veronica Meneghello, Loredana Pianta and Silvia Raimondi.
\end{itemize}

\noindent
And, finally, my wife. Amor, no est\'abamos casados cuando empec\'e a trabajar en esta tesis  en julio. Ahora que estoy escribiendo sus \'ultimas palabras, s\'i. No te puedo expresar lo maravillosa que eres y la felicidad que me embarga el compartir mi vida contigo. Gracias por haberme apoyado cuando decid\'i empezar este programa de estudios en Roma y durante los \'ultimos meses, en los cuales se sumaron mucho trabajo y viajes cansadores. Y, sobre todo, gracias por entender con sonrisas (y paciencia infinita) mi ser f\'isico te\'orico del alma, con las bromas aburridas y la l\'ogica insensata que conllevan. Te amo! \\

\noindent
Hannover, November 2017